\underline{Procedure}

For the second Electronics Lab, the objective is to solder RC circuits on a printed circuit board and then test the circuit as a Lowpass and Highpass Filter. To solder the resistor and capacitor, a soldering iron is used by melting metal onto the ends of the resistor and capacitor on a printed circuit board. After soldering, the output voltage in sine wave mode is measured at different frequencies using the oscilloscope. The Lowpass Filter has a function generator with internal resistance of (50\textOmega) which is in series with a 10k\textOmega resistor. The capacitor in this circuit is in parallel with the oscilloscope. The Highpass filter has a function generator with internal resistance of 50\textOmega  in series with a capacitor. The 10k\textOmega resistor is connected to the negative terminal of the function generator and is also in parallel with the oscilloscope. After taking the measurements, the transfer function ($H_{(s)} = \frac{V_o}{V_{in}$) for both filters are plotted as a function of frequency on a log-log scale. Lastly, the impulse response is measured by sending a pulse signal that is shorter than the RC time constant. The measured responses are then compared to the theoretical responses. \\
\\
\underline{LowPass Filter}
\\
\centerline{ $ H_{(s)} = \frac{V_o}{V_{in}} = \frac{Z_c}{Z_r + Z_c} $ }
\centerline{ $ Z_r = R, Z_c = \frac{1}{sc} $}
\centerline{ $ H_{(s)} = \frac{V_o}{V_{in}} = \frac{\frac{1}{sc}}{R + \frac{1}{sc}} $ }
\begin{equation}
\label{eq:LowPassFunction}
\centerline{ $ H_{(s)} = \frac{V_o}{V_{in}} = \frac{1}{sRC + 1} $ }
\end{equation}
\\
\underline{HighPass Filter}
\\
\centerline{ $ H_{(s)} = \frac{V_o}{V_{in}} = \frac{Z_r}{Z_r + Z_c} $ }
\centerline{ $ Z_r = R, Z_c = \frac{1}{sc} $}
\centerline{ $ H_{(s)} = \frac{V_o}{V_{in}} = \frac{R}{R + \frac{1}{sc}} $ }
\begin{equation}
\label{eq:HighPassFunction}
\centerline{ $ H_{(s)} = \frac{V_o}{V_{in}} = \frac{sRC}{sRC + 1} $ }
\end{equation}




